A Survey of Possible Exoskeleton Control Architectures and Algorithms\\ (Draft 2.1)

### 2015-09-20 control.tex
more updates

\title{A Survey of Possible Exoskeleton Control Architectures and
Algorithms\\
(Draft 2.0)}

@@

\section{Autonomous exoskeleton-world control}

\subsection{Autonomous exoskeleton-world position/velocity control}

A control objective could be to have the exoskeleton to move autonomously.

@@

@@

>>>>

\title{A Survey of Possible Exoskeleton Control Architectures and
Algorithms\\
(Draft 2.1)}

@@

\section{Autonomous exoskeleton control}

\subsection{Autonomous exoskeleton position/velocity control}

A control objective could be to have the exoskeleton to move autonomously,
which is useful if the operator would like to rest, is attending to some other
task, or is disabled.

This is usually done by using stored trajectories or trajectories generated
online that specify desired position $\vq_d$, 
desired velocity $\dot{\vq}_d$, and
desired acceleration $\ddot{\vq}_d$.
The feedforward method is to compute the needed torques (potentially offline)
using inverse
dynamics (including the operator link inertias, link centers of mass, and link
moments of inertia in the dynamic model) based on only the desired postion, 
desired velocity, and desired acceleration. Trajectory tracking errors are compensated
for by feedback control designed using some other method. In most robotics
fixed gain independent joint linear control is used.
This method is safest in the sense that the feedback controller can be tested
and verified independently of the desired trajectories and dynamic models.

Computed torque approaches use online inverse dynamics computed from the estimated
position, estimated velocity, and desired acceleration.
In this case the feedback control to compensate for trajectory tracking errors can
be independent of the inverse dynamics and its modeling errors, or the desired
acceleration can be modified with feedback terms.
\begin{equation}
\ddot{\vq}_d^* = \ddot{\vq}_{d} + \mK_{\vq}^{\ddot{\vq}} ( \hat{\vq} - \vq_d ) 
+ \mK_{\dot{\vq}}^{\ddot{\vq}} ( \hat{\dot{\vq}} - \dot{\vq_d} )
\end{equation}
The problem with putting the inverse dynamics in the feedback loop is that the
effective gains of this control vary widely with the configuration $\vq$.
Unmodeled dynamics (that also vary with $\vq$) limit the size of the gain matrices
$\mK_{\vq}^{\ddot{\vq}}$ and $\mK_{\dot{\vq}}^{\ddot{\vq}}$. Because so many quantities
are varying quite a bit, constant gain matrices may be quite low for a worst case
design. It is also very difficult to verify this type of nonlinear feedback controller.
For this reason most current approaches to humanoid
robots design the feedback controller
separately and use constant gain independent joint linear feedback control.

@@

\begin{verbatim}
include J' term
\end{verbatim}

Why isn't this identical to operator force control?

@@

\begin{verbatim}
Cartesis version - j-1
joint version, w jKj =k
\end{verbatim}

Why isn't this identical to operator impedance control?
